Classifier

### 2019-04-23 Code/dallin_annotations/07_build_classifier.Rmd
Added more documentation to file 07

# Train and Load the fastText Model
Unsupervised fastText models produce word vectors. In other words, the create a mathmatical representation of the word. 
```{r}
# Fasttext train ----------------------------------------------------------
# train unsupervised fasttext model to learn tweet semantics and word vector representations

# file to read tweets from. Should be a txt file with one tweet per line
# file_txt <- "../../Temporary/tweet_sample_2M_noRT.txt"
file_txt <- here::here("Temporary", "tweet_sample_1hM_noRT.txt")

@@

# train the unsupervised fasttext model
# I've commented out the training of this model because it has already been trained and the output has been saved to the Temporary folder.

# fastrtext::execute(commands = c("cbow", "-input", file_txt, "-output", file_model50, "-verbose", 1, "-dim", 50))

@@

# create a list column that contains all of features output by the fasttext model
train <- train %>%
  mutate(avg_vec_50 = map(tweet_text, VectorizeTweet, model = fasttext_model))

# Dallin: It looks like there is a problem with the map() or VectorizeTweet function above. 
# It doesn't seem to work well with mutate(). 
# I don't understand how Adriel got this to work. ¯\_(ツ)_/¯
# The little chunk below is myself troubleshooting an error.

# I tried troubleshooting the problem with this code below, but it didn't work well
# train <- train %>%
#      mutate(avg_vec_50 = map(tweet_text, avg_word_vec(text = ., model = fasttext_model)))

# I think I've fixed the problem by going into predict_func.R and removing the tbl_df() function and replacing it
# with the as_tibble() function. It looks like the documentation is saying that the tbl_df() function has been removed
# or something?
```

### Resulting Tweet Vectors
```{r}

@@

### Train PCA Model
```{r}
# select the average vector column and perform a PCA
train.pr <- train %>%
  select(avg_vec_50) %>% 
  unnest(avg_vec_50) %>% 
  as.matrix() %>% 
  prcomp()
```

### Evaluate the PCA Model with 3D Graph
```{r}
# create a dataframe with the pca output to examine the first 3 components

>>>>

# Train and Load the fastText Model
Unsupervised fastText models produce word vectors. In other words, the create a mathmatical representation of the word. These word vectors will be used later to 
```{r}
# Fasttext train ----------------------------------------------------------
# train unsupervised fasttext model to learn tweet semantics and word vector representations

# file to read tweets from. Should be a txt file with one tweet per line
file_txt <- here::here("Temporary", "tweet_sample_1hM_noRT.txt")

@@

# train the unsupervised fasttext model
# Note: I've commented out the training of this model because it has already been trained and the output has been saved to the Temporary folder.
# fastrtext::execute(commands = c("cbow", "-input", file_txt, "-output", file_model50, "-verbose", 1, "-dim", 50))

@@

# create a list column that contains all of features output by the fasttext model
train <- train %>%
  mutate(avg_vec_50 = map(tweet_text, VectorizeTweet, model = fasttext_model))
```

### Analyzing the Outputs of What We Did Above
The two sections below are the outputs of the code we ran above. for the example tweet first tweet, shown below.
```{r}
train$tweet_text[[1]]
```

##### Resulting Tweet Features
This is the output of the tweetFeatures() function. It just makes a small table of data explaining features of each tweet, such as the number of spaces, the number of exclamation points, the number of characters, etc. The data table shown below is the output for just one tweet. This small data table is then stored inside a list-column of the train data.
```{r}
train$tweetFeatures[[1]]
```

##### Resulting Tweet Vectors
Similar to the output above, this is the output of the VectorizeTweet() function for just one tweet. If you are familiar with word vectors, you will notice that this small data table looks similar to a single word vector. This vector, however, is a compilation of every word vector from each word in a given tweet. With the example tweet above, the VectorizeTweet() function finds the word vector for the words "two," "airports," "one," "greeen," etc. The VectorizeTweet() function takes the word vector for each word in the tweet and averages each column. In theory, this should provide a mathematical summary for the entire tweet.
```{r}
train$avg_vec_50[[1]]
```

@@

### Train PCA Model
This block of code trains the PCA model exclusively on the avg_vec_50 variable (the average tweet vector for each tweet).
```{r}
# select the average vector column and perform a PCA
train.pr <- train %>%
  select(avg_vec_50) %>% 
  unnest(avg_vec_50) %>% 
  as.matrix() %>% 
  prcomp()
```

### Evaluate the PCA Model with 3D Graph
Here, we create a dataframe with the PCA output for each tweet, paired with the tweet labels and tweet text. The data is then plotted with the three PCA variables on the axes, and color mapped to complaint type. With this visualization, we can see that the PCA model groups complaints and non-complaints well.
```{r}
# create a dataframe with the pca output to examine the first 3 components

### 2019-04-23 Paper/paper.Rmd
Added more documentation to file 07

To use our model, we feed a set of tweets into a PCA model and a FastText classification model. The output of these two models is then fed into our XGBoost model, which makes a binary prediction for the tweet as a complaint or non-complaint.

@@

# The FastText Sub-Model
## Overview
In this section, we'll be documenting how we built our model for classifying tweets as "complaints" and "non-complaints." The code is almost entirely derived from the Code/cnn-classifier/R/fasttext_supervised_classifier.R script.

@@

# The PCA Sub-Model
## Intro to PCA
The idea behind PCA is that a complex multi-dimensional problem can be boiled down to a single-dimensional problem. For example, what if you had a model that tried to predict a student's grade on a test by looking at how many hours the student studied, how many lectures the student attended, how many hours of sleep they got, what cereal they eat for breakfast, and how many siblings they have. While all of these factors could arguably have an affect on the student's test grade, I would expect the "hours studied" and "lectures attended" variables to have the strongest correlation to test. A PCA model would notice the most important variables of a model, and simplify the model to focus on just two "principle components" (note that it still incorporates the other variables in the model, but these variables have been "simplified" or "compressed")

@@

## Useful Resources:
Quick Explanation of PCA: https://www.youtube.com/watch?v=HMOI_lkzW08
https://www.youtube.com/watch?v=_UVHneBUBW0

>>>>

To use our model, we fed a set of tweets into a PCA model and a FastText classification model. The output of these two models is then fed into our XGBoost model, which makes a binary prediction for the tweet as a complaint or non-complaint.

@@

# The FastText Sub-Model
## Overview
In this section, we'll document how we built our model for classifying tweets as "complaints" and "non-complaints." The code is almost entirely derived from the Code/cnn-classifier/R/fasttext_supervised_classifier.R script.

@@

# The PCA Sub-Model
## Intro to PCA
The idea behind PCA is that a complex multi-dimensional problem can be boiled down to a single-dimensional problem. For example, let's say you had a model that tried to predict a student's grade on a test by looking at how many hours the student studied, how many lectures the student attended, how many hours of sleep they got, what cereal they eat for breakfast, and how many siblings they have. While all of these factors could arguably have an affect on the student's test grade, I would expect the "hours studied" and "lectures attended" variables to have the strongest correlation to test. A PCA model would notice the most important variables of a model, and simplify the model to focus on just two "principle components" (note that it still incorporates the other variables in the model, but these variables have been "simplified" or "compressed")

@@

## Useful Resources:
Quick Explanation of PCA: https://www.youtube.com/watch?v=HMOI_lkzW08
Deeper Explanation of PCA: https://www.youtube.com/watch?v=_UVHneBUBW0
